\documentclass{article}

\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{verse}
\usepackage{parskip}
\usepackage{ellipsis}
\usepackage{csquotes}
\usepackage{hyperref}

\newcommand{\titlevar}{A Quick Write-up of Pain}
\newcommand{\authorvar}{Günthner}
\newcommand{\datevar}{Winter 2024}
\title{\vspace{-2cm}\titlevar}
\author{\authorvar}
\date{\datevar}
\hypersetup{
	pdftitle=\titlevar,
	pdfauthor=\authorvar,
	pdfcreationdate=\datevar,
}
\setlength{\parindent}{0pt}

\newcommand{\fade}{\dots}

\begin{document}
	\maketitle
	
	We all carry our demons within. Also we all carry our angels within. It is our responsibility to distinguish them.
	
	\medskip
	
	The door opens as I enter our apartment. It was cold outside and I am glad to be back in the warmth together with the woman I love. We have only been together for a couple of months, but it was love on first sight and we have been living together ever since. Of course it wasn't all easy, but we have always been able to get through it all. So far this day has been absolutely lovely, getting up in the morning next to her, then, going through our daily routine together: Her writing all day and me cleaning the mess we made during the week. Before I went to get some cheese for us we—of course—coo'd at each other like the lovebirds we are. Now she is in front of me. Dead.
	
	\medskip
	
	\enquote{I had to do it.}—he said—\enquote{I couldn't let you take her from me!} This man in front of me is a \enquote{friend} of hers. At least that is what she always insisted on. Actually he had been stalking her for—well—the entire time we have been together. Before then he also was, but she still thought that that was normal. She has always had this idea—taught to her by her father—that everything other people do to her is alright and she just had to get a grip on herself and go along with it. Now it has finally caught up to her. And there is nothing I could do.
	
	\medskip
	
	Until now, she had always been able to convince me that the things he did to her, were no reason to go to the police. I was stupid. I was a fool.
	
	\medskip
	
	He has been touching her without consent, even when she fought him. He has been endangering her life, she could have died when he drove her onto the ice. How could I believe that not going to the police was an option? I feel guilty for her fate.
	
	\medskip
	
	This makes me wonder—once again—how he could overpower her. After all she is stronger than him, but then again—after all he did—she was always afraid to hurt him. Him. This monster.
	
	\medskip
	
	The past few week this sick idea had been haunting me: Killing him. Becoming the very creature he is. I again find myself tempted to loose myself.
	
	\pagebreak
	Instead I say: \enquote{You did have a choice.} The thoughts of murder evaporate and are replaced by calmness and peace. The peace that only a person's death can bring. \enquote{You always have a choice.}—\enquote{You don't understand! We had everything! It was all going so well before you came along and ruined everything!}—\enquote{You had nothing.}—I reply—\enquote{She never loved you and she never would have. All there ever was is your sick hunger for control. You always just wanted to be loved by somebody, but you weren't even ready to love them in return.}
	
	\medskip
	
	I take another second in my mind to think of something I can tell him that would make him understand. Make him understand. That is all I want now, no revenge, nothing, just that he understands and regrets what he has done to her—to us. I don't know whether something like that actually exists, making rapists and stalkers and murderers understand. But it is the only way I can pay him back in kind and get closure. What am I talking about!? I will never get closure! Not after something like this, but still I feel that I owe her—and all other victims—that I talk to him.
	
	\medskip
	
	He interrupts my thoughts: \enquote{Aren't you going to kill me now?} He seems surprised that I am not burning up in rage and tears and instead am bleeding a few sad and lone tears. \enquote{Wow, you really are a coward. Maybe I should have just visited you and convinced you to stay  away from my girlfriend.}—\enquote{How can you call her that after all you have done to her? After this? She was never your girlfriend just your victim. And she tought of you as a friend!}.—\enquote{She could have just gone away, if she didn't want what I gave her! It's her fault that I got so entranced with her! If she hadn't been as nice to me, I would have never even touched her!}
	
	\medskip
	
	\enquote{After all she has been through! You know her past as do I! You were always aware that she would not be able to say no! You used that and abused her! Do you seriously think that you are the first rapist to come up with that excuse?! Under the veil of \enquote{She could have stopped me} so many lives have been ruined! So many women—so many people have had their lives ruined, all because they didn't dare hit you when they—you—touched them! I know that you were well aware how it made her feel when you touched her, when you stroked her, when you rubbed yourself against her!}
	
	\medskip
	
	\enquote{But it isn't my fault that that happened to her. If it's anyone's, it is her's!}
	
	\medskip
	
	I feel alone. I always feel alone when some asshole says things this ignorant. It's because there nothing you can do to make them change their mind. Nothing you can say. They will always insist on their twisted understanding of the world.
	
	\medskip
	
	I can't believe that I once thought this way too.
	
	\pagebreak
	
	\enquote{Do you know why I can tell that you know what she felt when you abused her? It is because I have been to both worlds. Both sides.} \enquote{When I was a young child, just out of elementary school, I was abused by another child my age. I didn't really understand what she was doing and thought that I was supposed to like it when somebody touched me. After all that is what she told me as well.} \enquote{Over the years I developed sicker and sicker thoughts. You don't know how often I have thought about doing the very things that you have done. But you know what? It only ever felt good, when they—the victims in my head—were afraid. Their fear is what feeds these thoughts, it is how they come to be this strong.}
\end{document}
